Seniority and Hierarchy Configuration Interaction for Radicals and \\ Excited States

### 2023-08-28 Manuscript/manuscript.tex
capital letters
OK

\title{Seniority and hierarchy configuration interaction for radicals and \\ excited states}

@@

We have recently introduced a third CI route, hierarchy CI (hCI), \cite{Kossoski_2022}
where the Hilbert space is partitioned according to a hierarchy parameter $h$ that combines the excitation degree $e$ and the seniority number $s$ defined as $h = (e+s/2)/2$.
This definition ensures that all classes of determinants whose number share the same scaling with system size are included at the same hierarchy $h$.
\fk{This key feature distinguishes hCI from previous schemes combining excitation and seniority. \cite{Alcoba_2014,Raemdonck_2015,Alcoba_2018}
By allowing for higher-order excitations of paired electrons (as explained in detail below), hCI is reminiscent of perfect pairing models for closed-shell systems. \cite{Hurley_1953,Cullen_1996,VanVoorhis_2000,Parkhill_2009,Parkhill_2010,Lehtola_2016,Lehtola_2018}}
For different properties and closed-shell molecular systems,
hCI was found to display an overall faster convergence toward the FCI results than the traditional eCI route. \cite{Kossoski_2022}
In this sense, it was able to recover both static and dynamic correlations more effectively than either eCI or sCI.
However, hCI has only been defined for a closed-shell reference, thus being limited to the ground state of systems with an even number of electrons.

>>>>

\title{Seniority and Hierarchy Configuration Interaction for Radicals and \\ Excited States}

@@

We have recently introduced a third CI route, hierarchy CI (hCI), \cite{Kossoski_2022}
where the Hilbert space is partitioned according to a hierarchy parameter $h$ that combines the excitation degree $e$ and the seniority number $s$ defined as $h = (e+s/2)/2$.
This definition ensures that all classes of determinants whose number share the same scaling with system size are included at the same hierarchy $h$.
This key feature distinguishes hCI from previous schemes combining excitation and seniority. \cite{Alcoba_2014,Raemdonck_2015,Alcoba_2018}
By allowing for higher-order excitations of paired electrons (as explained in detail below), hCI is reminiscent of perfect pairing models for closed-shell systems. \cite{Hurley_1953,Cullen_1996,VanVoorhis_2000,Parkhill_2009,Parkhill_2010,Lehtola_2016,Lehtola_2018}
For different properties and closed-shell molecular systems,
hCI was found to display an overall faster convergence toward the FCI results than the traditional eCI route. \cite{Kossoski_2022}
In this sense, it was able to recover both static and dynamic correlations more effectively than either eCI or sCI.
However, hCI has only been defined for a closed-shell reference, thus being limited to the ground state of systems with an even number of electrons.
